The list of robot's main hardware components:

\begin{itemize}
  \item Raspberry Pi Model B Board
  \item Raspberry Pi No-IR Camera
  \item 2xEMG30 12v motor with encoder and 30:1 gearbox + mounting bracket
  \item Ultrasound Proximity sensor
  \item I2C Breakout Board
\end{itemize}

Insert images of the components (?).

\subsection*{Mechanical Part}

The robot is built on a metal frame with two driving wheels mounted on a EMG30
gearbox connected to the frame using the gearbox bracket. A metal ball wheel
located in front of the robot provides additional support. The frame consists of
metal profiles with a perforated plate that serves as a base for mounting
electronic components.

EMG30 is a module that incorporates motor, gearbox and encoder with Hall sensor
and suited for medium robotics applications. The gearbox provides increased
torque allowing robust movement in different environments while the Hall sensor
obtains information about the rotation of the shaft. (Include a reference to
the EMG30).



 

\subsection*{Electronics}

The main electronic component of the robot is the Raspberry Pi single-board
computer. Its technical specifications are listed in the Table
\ref{tab:rpi_specs}.

\begin{table}[h!]
	\setlength\extrarowheight{2pt}
    \begin{tabularx}{\textwidth}{XX}
    
    ~                 & ~                                                           \\
    System on a chip  & Broadcom BCM2835                                            \\
    CPU               & 700 MHz ARM11                                               \\
    GPU               & Broadcom VideoCore IV @ 250 MHz                             \\
    RAM               & 512 Mb shared with GPU                                      \\
    Memory            & SD Card Slot                                                \\
    Ports             & 2x USB, LAN, 3.5mm phone jack, HDMI,  GPIO (UART, I2C, SPI) \\
    Power Consumption & 700 mA (3.5 W)                                              \\
    
    \end{tabularx}
    \caption{Raspberry Pi Model B Specifications}
    \label{tab:rpi_specs}
\end{table}


The board is powered using 11.1V Turnigy LiPo Battery via power adapter that
splits the voltage into 12V (motors) and 5V lines. According to the external
power supply measurements, the average total consumption during movement is
(insert here).

The Raspberry Pi peripherals include a WiFi adapter, GPIO Breakout board for
simplifying connection, and a Raspberry Pi camera. RPi camera is a
board-specific 5Mp camera module connected via 15-pin MIPI (Mobile Industry
Processor Interface) connector. It is capable of capturing 1080p video and
perform basic hardware video processing. Two different types of cameras were
tested - standard camera and near-IR ``NoIR'' camera with the absence of
infrared filter. The performance of these cameras compared to standard USB
Webcam is shown in the Table \ref{tab:cam_perf}. In order to
increase the reliability and robustness of NoIR camera, a couple of IR LEDs were
installed to provide additional illumination.

Talk about sign design for the near-IR camera here.
After a series of experiments, a highly-reflective duct tape was chosen as a
material for the signs. It showed high reflectance under poor lighting
conditions. The usage of the NoIR camera accompanied with a couple of IR LEDs
showed high segmentation performance with minimum lighting provided.

MD25 is a dual H-Bridge I2C / Serial motor driver suited for the control of
EMG30 modules.
It provides additional capabilities in the motor manipulation, such as variable
acceleration, motor current information and independent control of two motors
with encoder feedback. It is also equipped with a 5V regulator, however it is
impossible to power the Raspberry Pi as the continuous supply rate is 300 mA,
while the average consumption of Raspberry Pi is 700 mA.

Put the reference.
\url{http://www.pishrobot.com/files/products/datasheets/md25.pdf}

Due to the reason explained before, Raspberry Pi is powered using Taco Power TSR
1-2450 DC-DC voltage step-down modules that provide 5V 1A output.

Put the reference.
\url{http://www.adafruit.com/datasheets/tsr1.pdf}

% Fix table here
\begin{table}[h!]
	\setlength\extrarowheight{2pt}
	\setlength\arraycolsep{5pt}
    \begin{tabularx}{\textwidth}{XXXX}
    Resolution / Camera Setup & Raspberry Pi  (CPU) + Raspberry Pi Camera &
    Raspberry Pi (CPU) + Logitech C270 & Odroid-U3 (CPU) + Logitech C270 \\
    160x120            & 18           & 9          & 30         \\
    320x240            & 6            & 4.8        & 20         \\
    640x480            & 2.5          & 2.3        & 11         \\
    1280x720           & 0.6          & 0.8        & 4          \\
    \end{tabularx}
    \caption{Camera Performance comparison}
    \label{tab:cam_perf}
\end{table}

As can be seen from the Table \ref{tab:cam_perf}, the main advantage of using
RPi camera is its performance - it outperforms generic Webcam grace to hardware
optimization and, in particular, absence of resizing routine in the code.
However, the disadvantage lies in the specificity of the camera, that can only
be used on the RPi board, while the USB Webcam can be used everywhere, so in
order to port the code to another platform, the camera change as well as some
code modification are required.

The robot is also equipped with an ultrasound proximity sensor used for obstacle
detection. It is a basic proximity sensor with a focus of 15 degrees and an
accuracy about 2mm. 

An I2C LCD Screen module provides an interface for visual feedback.